Supporting Information

### 2020-04-24 documents/reviewer-responses.Rmd

---
title: "Reviewer Responses for 'The Population Effects of Marine Protected Areas Are Likely To Be Unclear' (previously 'The Regional Effects of MPAs')"
author: 
  - Daniel Ovando
  - Jennifer E. Caselle
  - Christopher Costello
  - Olivier Deschenes
  - Steven D. Gaines
  - Ray Hilborn
  - Owen Liu
output:
  word_document: default
  html_document: default
  pdf_document: default
bibliography: My Library.bib
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reviewer Responses

We thank the two reviewers and the Editor for their constructive responses. We have fundamentally restructured the paper to place much greater emphasis on the results from the Channel Islands Marine Protected Area (MPA) network. This is to our knowledge the first empirical assessment of the regional effects of a large and iconic MPA network on a wide assemblage of commercially and economically important species. Our inability to estimate a clear population-level effect in such a well-enforced and well-studied location is we feel an important "null-result" both for scientists and MPA managers to be aware of. As such we hope that it warrants publication in PNAS.

@@

While our results are more focused on the empirical results, we explicitly link our results to the large body of MPA theoretical work, using it to help illustrate why we might expect such a null result and help managers understand when they might be able to detect an effect. As MPAs are used as a core tool of marine resource management, our results provide a useful update to our empirical expectations for MPAs, that to date have been based almost entirely on inside-outside MPA response ratios.

As pointed out by the reviewers, many of the more theoretical points we make about the importance of fleet dynamics and the challenges of response ratios have been made in the past. However, we feel there is substantial value in revisiting those discussions in the context of a concrete empirical example, to provide scientists and practitioners alike a cohesive reference to observe and understand the full ramifications of these past findings on our practical ability to monitor and manage marine protected area networks. We have strived to make clearer though that the theoretical section is a reflection of broad body of theoretical work.

### 2020-04-24 documents/ovando-et-al-pop-effects-of-mpas-si.Rmd
got synthetic controls working again

---
title: "Supporting Information: Population Effects of Marine Protected Areas Are Likely To Be Unclear"
author: 
  - Daniel Ovando
  - Jennifer E. Caselle
  - Christopher Costello
  - Olivier Deschenes
  - Steven D. Gaines
  - Ray Hilborn
  - Owen Liu
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    keep_tex: true
  pdf_document: default
bibliography: My Library.bib
header-includes:
    - \usepackage{longtable}
    - \usepackage{booktabs}
    - \usepackage{eso-pic}
    - \usepackage{graphicx}
    - \usepackage[left]{lineno}
    - \usepackage{xcolor}
params:
  run_name: ["v6.0"]
  sim_years: [50]
  burn_years: [20]
  num_patches: [25]
always_allow_html: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 600,
                      cache = FALSE, fig.width = 7, fig.asp = .75)

@@

```{r, include=FALSE}
library(sf)
library(ggmap)
library(viridis)
library(hrbrthemes)
library(scales)
library(patchwork)
library(rpart)
library(extrafont)
library(caret)
library(ggsci)
library(rEDM)
library(tidyverse)
library(ggtext)
library(rstan)
library(rstanarm)
library(bayesplot)
extrafont::loadfonts()
rstan_options(auto_write = TRUE)

@@

@@

@@

The difference-in-difference model also assumes that the targeted and non-targeted fishes do not directly or indirectly affect each other.This assumption is clearly violated on some level: all the fishes in this analysis are part of the same ecosystem and therefore interact to some degree. For example, if the protection of targeted predatory fishes results in increased mortality of non-targeted fishes, the model would attribute that as an increased regional effect (greater divergence between the abundance of targeted and non-targeted species). Given the time scale of analysis (15 years of protection), we do not feel that massive trophic cascades are likely to have developed yet, given both the pace and complexity of trophic cascade development [@babcock2010; @pershing2015a]. A complete assessment of evidence for trophic cascades in the Channel Islands is beyond the scope of this study, but to address this question somewhat we utilized convergent cross mapping *sensu* @sugihara2012 to test for a significant causal signal between different broad trophic groups in the data, implemented in the `rEDM` package in R.

@@

@@

```{r pop-conservation-effect, include = TRUE, fig.cap="Median (A) and range (B) of equilibrium regional MPA conservation effects (change in total biomass with MPAs relative to without MPAs as a percentage of unfished biomass) across a range of depletion and MPA sizes (and incorporating the full range of scenarios included in our study). 'Range in MPA' is the percent of patches covered by an MPA, 'Depletion' is the depletion that would have occurred in equilibrium without the MPA"}

>>>>

---
title: "Supporting Information"
subtitle: "Assessing the Population-level Conservation Effects of Marine Protected Areas"
author: 
  - Daniel Ovando
  - Jennifer E. Caselle
  - Christopher Costello
  - Olivier Deschenes
  - Steven D. Gaines
  - Ray Hilborn
  - Owen Liu
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    keep_tex: true
  pdf_document: default
bibliography: My Library.bib
header-includes:
    - \usepackage{longtable}
    - \usepackage{booktabs}
    - \usepackage{eso-pic}
    - \usepackage{graphicx}
    - \usepackage[left]{lineno}
    - \usepackage{xcolor}
params:
  run_name: ["v6.0"]
  sim_years: [50]
  burn_years: [20]
  num_patches: [25]
always_allow_html: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 600,
                      cache = FALSE, fig.width = 7, fig.asp = .75,
                      dev = "cairo_pdf")

@@

```{r, include=FALSE}
library(sf)
library(ggmap)
library(viridis)
library(hrbrthemes)
library(scales)
library(patchwork)
library(rpart)
library(extrafont)
library(caret)
library(ggsci)
library(rEDM)
library(tidyverse)
library(ggtext)
library(rstan)
library(rstanarm)
library(bayesplot)
library(Synth)

extrafont::loadfonts()
rstan_options(auto_write = TRUE)

@@

It is important to note that this model asks a slightly different question than our base model. The base model estimates the effect on total mean biomass of targeted finfish at the site level. This model estimates the effect on the mean biomass density of targeted finfish across all sites.

@@

### Synthetic controls

Synthetic controls are an alternative method for attempting to estimate the causal effect of a policy intervention [@abadie2010]. A difference-in-difference approach assumes that some observable group serves as an adequate control for the state of the treated group in an untreated world. In our default case, we assume that the mean standardized index of non-targeted species are our control for the targeted species. Alternatively, synthetic controls use timeseries of treated and non-treated groups before and after treatment to construct a new "control" group built by weighting the pre-treatment timeseries of un-treated observations (together with covariates) such that the synthetic control group matches the trends in the treated group pre-treatment.

We chose to present difference-in-difference as our main result since it better allows us to capture the uncertainty in the data generating process through our hierarchical model. However, we felt that it was worth exploring whether synthetic controls provided substantially different results than our default model.

For the first synthetic control, we pulled our standardized mean index of abundance for targeted species as a whole from our difference-in-difference model as our treated group. We then pull the standardized indices of abundance for each of the non-targeted groups from the difference-in-difference to use as the candidate untreated components for the synthetic controls. A complete synthetic control analysis would require more extensive validation of the methods, but we use this approach simply to explore whether we observe substantially divergent results in the synthetic control versus the difference-in-difference model.

We centered and scaled the candidate abundance indices to facilitate model convergence given the very few number of pre-treatment years available. The results of a synthetic control model are presented as the difference between the observed treatment outcome and the synthetic control (the difference in this case being in units of standard deviations). The model was not able to construct an adequate synthetic control at this level, as shown by the differences between the treated group and the synthetic control pre-treatment. However, we would note that the post-treatment results do show similarities with our main results, namely a lack of a clear divergence between the treatment and the control, and an upwards trend up through the earl 2010s followed by a decline (Fig.S\@ref(fig:total-synth)).

```{r, include = FALSE}

years <- unique(used_data$year)

life_history <- used_data %>%
  select(classcode) %>%
  unique() %>%
  mutate(numeric_classcode = as.numeric(as.factor(classcode)))

nontargeted_index <- data_frame(abundance_hat = fit_report$abundance_hat,
                               classcode = rep(1:n_distinct(used_data$classcode), each = length(years))) %>%
  mutate(log_abundance_hat = log(abundance_hat)) %>%
  group_by(classcode) %>%
  mutate(year =years) %>%
  mutate(scaled_abundance_hat = (abundance_hat - mean(abundance_hat)) / sd(abundance_hat)) %>%
  ungroup() %>%
  rename(numeric_classcode = classcode) %>%
  left_join(life_history, by = "numeric_classcode" ) %>% 
  left_join(unique(abundance_data$data[[1]] %>% select(classcode, targeted)), by = "classcode") %>% 
  filter(targeted == 0) %>% 
  select(log_abundance_hat, year, classcode, targeted)

targeted_index <- tmb_runs$tmb_fit[[1]]$zissou_estimates %>%
  filter(
    stringr::str_detect(variable, "(targeted_did_betas)"),!str_detect(variable, "non")
  ) %>%
  mutate(
    year = years,
    classcode = "targeted",
    targeted = 1
  ) %>%
  rename(log_abundance_hat = estimate) %>% 
  select(colnames(nontargeted_index))

  # filter(variable == "seeing_year_species_betas") %>%

nontargeted_covariates <- used_data %>% 
  select(classcode, contains("mean"),year, targeted) %>% 
  filter(targeted == 0) %>% 
  select(-mean_length) %>% 
  gather(variable, value, -classcode,-year,-targeted) %>% 
  group_by(classcode, variable, year) %>% 
  summarise(mean_value = mean(value, na.rm = TRUE)) %>% 
  spread(variable, mean_value)

targeted_covariates <- used_data %>% 
  select(classcode, contains("mean"),year, targeted) %>% 
  filter(targeted == 1) %>% 
  mutate(classcode = "targeted") %>% 
  select(-mean_length) %>% 
  gather(variable, value, -classcode,-year,-targeted) %>% 
  group_by(classcode, variable, year) %>% 
  summarise(mean_value = mean(value, na.rm = TRUE)) %>% 
  spread(variable, mean_value)

synth_covariates <- nontargeted_covariates %>% 
  bind_rows(targeted_covariates)

synth_data <- targeted_index %>% 
  bind_rows(nontargeted_index) %>% 
  left_join(synth_covariates, by = c("classcode","year")) %>% 
    mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
  group_by(classcode) %>% 
  mutate(log_abundance_hat = scale(exp(log_abundance_hat))) %>% 
  ungroup() %>% 
  as.data.frame() %>% 
  select(-rolling_mean)

# synth_data %>%
#   group_by(classcode) %>%
#   mutate(index = (log_abundance_hat)) %>%
#   ggplot(aes(
#     year,
#     index,
#     color = factor(targeted),
#     group = interaction(targeted, classcode)
#   )) +
#   geom_line()

prepped_synth_data <-
  Synth::dataprep(
    foo = synth_data,
    predictors = colnames(synth_data)[str_detect(colnames(synth_data),"mean")],
    predictors.op = "mean",
    dependent = "log_abundance_hat",
    unit.variable = "numeric_classcode",
    unit.names.variable = "classcode",
    time.variable = "year",
    treatment.identifier = "targeted",
    controls.identifier = unique(synth_data$classcode)[unique(synth_data$classcode) != "targeted"],
    time.predictors.prior = years[years <= 2003],
    time.optimize.ssr = years[years <= 2003],
    time.plot = years
  )

synth_fit <- Synth::synth(prepped_synth_data)

gaps <-
  rownames_to_column(
    prepped_synth_data$Y1plot - (prepped_synth_data$Y0plot %*% synth_fit$solution.w) %>%
      as.data.frame()
  ) %>%
  rename(gap = w.weight,
         year = rowname) %>%
  mutate(year = as.numeric(year)) %>%
  mutate(synthetic = as.numeric(prepped_synth_data$Y0plot %*% synth_fit$solution.w)) %>% 
  mutate(treatment = gap + synthetic)

# path.plot(synth.res = synth_fit,
#           dataprep.res = prepped_synth_data
# )

total_gap_plot <- gaps %>% 
  ggplot(aes(year, gap)) + 
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_vline(aes(xintercept = 2003), color = "red")+
  geom_line() + 
    labs(x = "Year", y = "Standard deviations from synthetic control")

total_synth_plot <- gaps %>% 
  select(year, synthetic, treatment) %>% 
  gather(source, value, -year) %>% 
  group_by(source) %>% 
  # mutate(value = scale(value)) %>% 
  ggplot(aes(year, value, color = source, linetype = source)) + 
  geom_vline(aes(xintercept = 2003), color = "red")+
  geom_line() + 
    labs(x = "Year", y = "Standard deviations from synthetic control")

```{r raw-synth, include = FALSE}

years <- unique(used_data$year)

life_history <- used_data %>%
  select(classcode) %>%
  unique() %>%
  mutate(numeric_classcode = as.numeric(as.factor(classcode)))

nontargeted_index <- data_frame(abundance_hat = fit_report$abundance_hat,
                               classcode = rep(1:n_distinct(used_data$classcode), each = length(years))) %>%
  mutate(log_abundance_hat = log(abundance_hat)) %>%
  group_by(classcode) %>%
  mutate(year =years) %>%
  mutate(scaled_abundance_hat = (abundance_hat - mean(abundance_hat)) / sd(abundance_hat)) %>%
  ungroup() %>%
  rename(numeric_classcode = classcode) %>%
  left_join(life_history, by = "numeric_classcode" ) %>% 
  left_join(unique(abundance_data$data[[1]] %>% select(classcode, targeted)), by = "classcode") %>% 
  filter(targeted == 0) %>% 
  select(log_abundance_hat, year, classcode, targeted)

targeted_index <- tmb_runs$tmb_fit[[1]]$zissou_estimates %>%
  filter(
    stringr::str_detect(variable, "(targeted_did_betas)"),!str_detect(variable, "non")
  ) %>%
  mutate(
    year = years,
    classcode = "targeted",
    targeted = 1
  ) %>%
  rename(log_abundance_hat = estimate) %>% 
  select(colnames(nontargeted_index))

  # filter(variable == "seeing_year_species_betas") %>%

nontargeted_covariates <- used_data %>% 
  select(classcode, contains("mean"),year, targeted) %>% 
  filter(targeted == 0) %>% 
  select(-mean_length) %>% 
  gather(variable, value, -classcode,-year,-targeted) %>% 
  group_by(classcode, variable, year) %>% 
  summarise(mean_value = mean(value, na.rm = TRUE)) %>% 
  spread(variable, mean_value)

targeted_covariates <- used_data %>% 
  select(classcode, contains("mean"),year, targeted) %>% 
  filter(targeted == 1) %>% 
  mutate(classcode = "targeted") %>% 
  select(-mean_length) %>% 
  gather(variable, value, -classcode,-year,-targeted) %>% 
  group_by(classcode, variable, year) %>% 
  summarise(mean_value = mean(value, na.rm = TRUE)) %>% 
  spread(variable, mean_value)

synth_covariates <- nontargeted_covariates %>% 
  bind_rows(targeted_covariates)

synth_data <- targeted_index %>% 
  bind_rows(nontargeted_index) %>% 
  left_join(synth_covariates, by = c("classcode","year")) %>% 
    mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
  group_by(classcode) %>% 
  mutate(log_abundance_hat = scale(exp(log_abundance_hat))) %>% 
  ungroup() %>% 
  as.data.frame() %>% 
  select(-rolling_mean)

# synth_data %>%
#   group_by(classcode) %>%
#   mutate(index = (log_abundance_hat)) %>%
#   ggplot(aes(
#     year,
#     index,
#     color = factor(targeted),
#     group = interaction(targeted, classcode)
#   )) +
#   geom_line()

prepped_synth_data <-
  Synth::dataprep(
    foo = synth_data,
    predictors = colnames(synth_data)[str_detect(colnames(synth_data),"mean")],
    predictors.op = "mean",
    dependent = "log_abundance_hat",
    unit.variable = "numeric_classcode",
    unit.names.variable = "classcode",
    time.variable = "year",
    treatment.identifier = "targeted",
    controls.identifier = unique(synth_data$classcode)[unique(synth_data$classcode) != "targeted"],
    time.predictors.prior = years[years <= 2003],
    time.optimize.ssr = years[years <= 2003],
    time.plot = years
  )

synth_fit <- Synth::synth(prepped_synth_data)

gaps <-
  rownames_to_column(
    prepped_synth_data$Y1plot - (prepped_synth_data$Y0plot %*% synth_fit$solution.w) %>%
      as.data.frame()
  ) %>%
  rename(gap = w.weight,
         year = rowname) %>%
  mutate(year = as.numeric(year)) %>%
  mutate(synthetic = as.numeric(prepped_synth_data$Y0plot %*% synth_fit$solution.w)) %>% 
  mutate(treatment = gap + synthetic)

# path.plot(synth.res = synth_fit,
#           dataprep.res = prepped_synth_data
# )

total_gap_plot <- gaps %>% 
  ggplot(aes(year, gap)) + 
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_vline(aes(xintercept = 2003), color = "red")+
  geom_line() + 
    labs(x = "Year", y = "Standard deviations from synthetic control")

total_synth_plot <- gaps %>% 
  select(year, synthetic, treatment) %>% 
  gather(source, value, -year) %>% 
  group_by(source) %>% 
  # mutate(value = scale(value)) %>% 
  ggplot(aes(year, value, color = source, linetype = source)) + 
  geom_vline(aes(xintercept = 2003), color = "red")+
  geom_line() + 
    labs(x = "Year", y = "Standard deviations from synthetic control")

```{r  total-synth, fig.cap = "Difference in centered and scaled standardized targeted abundance and synthetic standardized targeted abundance"}
total_gap_plot
```

As an extension, we repeated this process, but now treating each targeted species individually as the treated group, and the non-targeted species as the non-targeted. This is intended to explore whether we see clearer signals for individual species than we do for the targeted class as a whole.

Overall we see similarly unclear results as the aggregate targeted synthetic control (and our main results). The synthetic control was better constructed for some individual species, but not clearly for any one, and most species showed some evidence of the upward-then-downward trend seen throughout our results (Fig.S\@ref(fig:synth-classcode-fits)).

```{r, include = FALSE}

synth_foo <-
  function(treated_classcode,
           synth_data,
           targeted_classcodes) {
    # treated_classcode <- targeted_classcodes[1]

    temp_synth_data <- synth_data %>%
      filter(classcode == treated_classcode |
               !(classcode %in% targeted_classcodes))

    prepped_synth_data <-
      Synth::dataprep(
        foo = temp_synth_data,
        predictors = colnames(temp_synth_data)[str_detect(colnames(temp_synth_data), "mean")],
        predictors.op = "mean",
        dependent = "log_abundance_hat",
        unit.variable = "numeric_classcode",
        unit.names.variable = "classcode",
        time.variable = "year",
        treatment.identifier = treated_classcode,
        controls.identifier = unique(temp_synth_data$classcode)[unique(temp_synth_data$classcode) != treated_classcode],
        time.predictors.prior = c(2000:2003),
        time.optimize.ssr = c(2000:2003),
        time.plot = years
      )

    synth_fit <- Synth::synth(prepped_synth_data)

    gaps <-
      rownames_to_column(
        prepped_synth_data$Y1plot - (prepped_synth_data$Y0plot %*% synth_fit$solution.w) %>%
          as.data.frame()
      ) %>%
      rename(gap = w.weight,
             year = rowname) %>%
      mutate(year = as.numeric(year)) %>%
      mutate(synthetic = as.numeric(prepped_synth_data$Y0plot %*% synth_fit$solution.w)) %>%
      mutate(treatment = gap + synthetic)
  }

nontargeted_index <- data_frame(abundance_hat = fit_report$abundance_hat,
                               classcode = rep(1:n_distinct(fitted_data$classcode), each = length(years))) %>%
  mutate(log_abundance_hat = log(abundance_hat)) %>%
  group_by(classcode) %>%
  mutate(year = 1999 + 1:length(abundance_hat)) %>%
  mutate(scaled_abundance_hat = (abundance_hat - mean(abundance_hat)) / sd(abundance_hat)) %>%
  ungroup() %>%
  rename(numeric_classcode = classcode) %>%
  left_join(life_history, by = "numeric_classcode" ) %>% 
  left_join(unique(abundance_data$data[[1]] %>% select(classcode, targeted)), by = "classcode") %>% 
  select(log_abundance_hat, year, classcode, targeted)

synth_covariates <- pisco_data %>% 
  select(classcode, contains("mean"),year, targeted) %>% 
  select(-mean_length) %>% 
  gather(variable, value, -classcode,-year,-targeted) %>% 
  group_by(classcode, variable, year) %>% 
  summarise(mean_value = mean(value, na.rm = TRUE)) %>% 
  spread(variable, mean_value)

synth_data <- nontargeted_index %>% 
  left_join(synth_covariates, by = c("classcode","year")) %>% 
    mutate(numeric_classcode = as.numeric(factor(classcode))) %>% 
  group_by(classcode) %>% 
  mutate(log_abundance_hat = scale(exp(log_abundance_hat))) %>% 
  ungroup() %>% 
  as.data.frame()

targeted_classcodes <- unique(synth_data$classcode[synth_data$targeted == 1])

synth_classcode_fits <-
  tibble(targeted_classcodes = targeted_classcodes) %>%
  mutate(
    synthetic_fit = map(
      targeted_classcodes,
      synth_foo,
      synth_data = synth_data,
      targeted_classcodes = targeted_classcodes
    )
  )

synth_classcode_fits <- synth_classcode_fits %>% 
  unnest()

synth_classcode_fits_plot <- 
synth_classcode_fits %>% 
  ggplot(aes(year, gap)) + 
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_vline(aes(xintercept = 2003), color = "red")+
  geom_line() + 
  facet_wrap(~targeted_classcodes) + 
  labs(x = "Year", y = "Standard deviations from synthetic control")

```{r synth-classcode-fits, fig.cap="Synthetic control gaps for each targeted species"}
synth_classcode_fits_plot + 
  theme_minimal()
```

@@

The difference-in-difference model also assumes that the targeted and non-targeted fishes do not directly or indirectly affect each other.This assumption is clearly violated on some level: all the fishes in this analysis are part of the same ecosystem and therefore interact to some degree. For example, if the protection of targeted predatory fishes results in increased mortality of non-targeted fishes, the model would attribute that as an increased population effect (greater divergence between the abundance of targeted and non-targeted species). Given the time scale of analysis (15 years of protection), we do not feel that massive trophic cascades are likely to have developed yet, given both the pace and complexity of trophic cascade development [@babcock2010; @pershing2015a]. A complete assessment of evidence for trophic cascades in the Channel Islands is beyond the scope of this study, but to address this question somewhat we utilized convergent cross mapping *sensu* @sugihara2012 to test for a significant causal signal between different broad trophic groups in the data, implemented in the `rEDM` package in R.

@@

The model consists of 50 patches with wrapped edges (picture the waters around a circular island). For any one simulation we randomly pull a species and its associated life history from the `FishLife` [@thorson2017c] package in R. We pair these data with randomly selected values between 0.6 and 0.95 for Beverton-Holt steepness [as parameterized in @mace1994], as well as larval and adult dispersal rates. We randomly assign whether adult fish preferentially move towards patches with lower relative densities, as well as one of three potential types of recruitment density dependence [building off of @babcock2011]. Simulations are also assigned random fleet dynamics (open access ,constant effort, constant catch), responses to MPA (leave the fishery or concentrate outside MPAs), a fleet dispersal model (uniform in response to catch-per-unit-effort, in response to profit-per-unit-effort)

<!--   1. Local density dependence: Density dependence occurs independently in each patch, and recruits then disperse to nearby patches -->

<!--   2. Global density dependence: Density dependence is a function of the sum of spawning biomass across all patches, and recruits are then distributed according to habitat quality -->

<!--   3. Post-dispersal density dependence: Larvae are distributed throughout the system, and then density dependence occurs based on the density of adult biomass at the destination patch -->

<!-- We allow for three potential siting strategies for MPAs. In the first, MPAs are randomly placed. In the second, we assume that MPAs are placed in preferentially better habit (unfished recruitment is four times greater inside MPA locations). In the third, we allow for scenarios in which MPAs are placed in sources of larval dispersal. -->

<!-- Each simulation is randomly assigned a fleet model of the form  -->

<!--   1. Open access: fishing effort changes in response to profit-per-unit-effort -->

<!--   2. Constant effort: total fishing effort is constant over time (unless altered by MPA displacement model) -->

<!--   3. Constant catch: the fleet exerts as much effort as need to achieve a target catch -->

<!-- This fleet model is paired with a gear selectivity ranging from .1 to 1.5 of the length at 50% maturity for the species in question, and the fleet model is tuned to achieve a target fishing mortality relative to natural mortality ratio at equilibrium. -->

<!-- Along with the fleet dynamics model, each simulation is assigned a random fleet dispersal scenario: uniform dispersal (where the total effort of the fleet is divided evenly among all open patches), catch dispersal (where the total effort of the fleet is divided according to the catchable biomass in each available patch), and profit dispersal (where the total effort of the fleet is divided according to the profit per unit effort in each available patch). Fishing effort that occurred inside MPAs prior to closer can either leave the fishery, or be distributed to the patches outside the MPAs. -->

Each simulation is assigned an MPA scenario, defined by the number and size of MPAs, the placement of those MPAs, and the year that the MPAs are put in place. The population begins at unfished equilibrium and then fishing effort is applied in accordance to the fleet model. The MPAs are then placed during the randomly selected start year, allowing some runs to explore how the early dynamics of the MPA play out when the fishery and population they are placed on is not already at equilibrium. Each simulation is run to equilibrium with and without the selected MPA strategy (holding all else constant). We then measure the difference in biomass densities each time step in the scenario with and without the MPAs to calculate the population effect of the MPAs over time.

@@

```{r pop-conservation-effect, include = TRUE, fig.cap="Median (A) and range (B) of equilibrium population-level MPA conservation effects (change in total biomass with MPAs relative to without MPAs as a percentage of unfished biomass) across a range of depletion and MPA sizes (and incorporating the full range of scenarios included in our study). 'Range in MPA' is the percent of patches covered by an MPA, 'Depletion' is the depletion that would have occurred in equilibrium without the MPA"}
